---
title: "Vignette"
author: "Sharene Siddiqui"
date: "5/3/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial 

The package `"binomial"` implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.


## Calculate the number of combinations in which k successes can occur in n trials

```{r}
bin_choose(n, k)
```

There are no defaults so you must define your n and k


## Probability of getting k successes in n trials 

```{r}
bin_probability(k, n, p)
```

There are no defaults so you must define your k, n, and p.

## Graphs a barplot to display the probability histogram of a binomial distribution

```{r}
dis1 <- bin_distribution(n, p)
plot.bindis(dis1)
```


## Graphs the cumulative distribution

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of coin tosses:

```{r}
dis2 <- bin_cumulative(n, p)
plot.bincum(dis2)
```